% Soonho Kong
% CV in LaTeX
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, letterpaper]{article}
\usepackage[no-math]{fontspec}
\usepackage{MnSymbol}
\usepackage{color}
\usepackage{enumerate}
\usepackage{ifsym}
\usepackage{marvosym}
\usepackage{bibentry}
\usepackage{xspace}

\usepackage[backend=biber, style=numeric-comp, sorting=ydnt, maxnames=20, url=false, doi=false, isbn=false, useeditor=false]{biblatex}

\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\addbibresource{publications.bib}

% TODO(soonho): Handle this.
% \addbibresource{patents.bib}

\input{dvipsnam.def}
\synctex=1

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\labelitemi}{$\blacktriangleright$}
\newcommand{\kwang}{Prof. Kwangkeun Yi}
\newcommand{\emc}{Prof. Edmund M. Clarke}
\newcommand{\USD}{\textdollar}
\newcommand{\interval}[2]
{#1 -- \makebox[1.5cm]{\hfill#2}}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
% \setromanfont[Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
\setmonofont[Scale=0.8]{Monaco}
\setsansfont[Scale=0.9]{Optima Regular}
% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}\xspace}
% ---- MARGIN YEARS
\newcommand{\years}[1]{\marginpar{\scriptsize #1}}

% Take out "References"
\renewcommand\refname{}

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\scshape\normalsize}
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize}

\newcommand{\mysection}[1]{
  \vspace{20pt}\noindent{\rmfamily\mdseries \Large #1}\\
  \vspace{-6pt}\hrule\vspace{3pt}
}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[bookmarks, breaklinks,
pdftitle={Soonho Kong - vita},pdfauthor={Soonho Kong}]{hyperref}

\setlength{\leftmargini}{15pt}

% DOCUMENT
\begin{document}
\reversemarginpar
{\huge Soonho Kong}\\[0.4cm]
Senior Applied Scientist at \href{https://aws.amazon.com}{Amazon Web Services}\\
Email: \url{soonho.kong@gmail.com}\\
Web: \url{https://soonhokong.github.io}\\
Github: \url{https://github.com/soonhokong}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{Research Interests}

My research focuses on the design and implementation of AI systems
with formal reasoning capabilities. In particular, I’m interested in
combining LLMs with interactive and automated theorem proving
techniques to achieve this goal.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{Work Experience}
 - Amazon Web Services (Sep 2021 -- Present)\\
 - Toyota Research Institute (Aug 2016 -- Sep 2021)


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{Education}
\textbf{Carnegie Mellon University} \\
Ph.D. in Computer Science \\
Advisor: \emc
\vspace{0.5em}

\textbf{Seoul National University} \\
Master of Science in Computer Science and Engineering\\
Advisor: \kwang
\vspace{0.5em}

\textbf{Seoul National University}\\
Bachelor of Science in Computer Science and Engineering

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{Software}
\href{https://github.com/dreal/dreal4}{\textbf{dReal}}: SMT solver for nonlinear theories over the Reals \hfill (Lead developer, since 2013)\\
\href{https://drake.mit.edu}{\textbf{Drake}}: Model-based design and verification for robotics \hfill (Platform-reviewer, 2017 -- 2021)\\
\href{https://leanprover.github.io}{\textbf{Lean}}: Lean theorem prover \hfill (Contributor, 2013 -- 2016)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\mysection{Publications}


\nocite{*}
\printbibliography[heading=none]

\mysection{Patents}

\begin{thebibliography}{9}

\bibitem{P0} ``Wearable exoskeleton''.
Jonathan DeCastro, Soon Ho Kong, Nikos Gonzalez Arechiga, Frank Permenter, and Dennis Park
United States Patent \#11918535. March 2024.

\bibitem{P1} ``Actively adapting to driving environments based on human interactions''.
Soonho Kong, Jonathan DeCastro, Nikos Arechiga, and Frank Permenter
United States Patent \#11801852. October 2023.

\bibitem{P2}``Certified control for self-driving cars''.
Daniel Jackson, Jonathan Decastro, Soon Ho Kong, Nikos Arechiga Gonzalez, Dimitrios Koutentakis, Feng Ping Angela Leong, Mike Meichang Wang, And Xin Zhang
United States Patent \#11745732. September 2023.

\bibitem{P3}``Predictive impairment monitor system and method''.
Nikos Gonzalez Arechiga, Soon Ho Kong, Jonathan DeCastro, Frank Permenter, and Dennis Park
United States Patent \#11518408. December 2022.

\bibitem{P4}``Predictive parking due to weather''.
Nikos Gonzalez Arechiga, Soon Ho Kong, Jonathan DeCastro, Frank Permenter, and Dennis Park
United States Patent \#11479239. October 2022.

\bibitem{P5}``Simulation-based Technique to Synthesize Controllers that Satisfy Signal Temporal Logic Specifications''.
Nikos Arechiga, Karen Y. Leung, Soon Ho Kong, Jonathan Decastro, and Frank Permenter
United States Patent \#11256611. February 2022.

\bibitem{P6}``System and Method for Detecting Errors and Improving Reliability of Perception Systems Using Logical Scaffolds''.
Nikos Arechiga, Soonho Kong, Jonathan DeCastro, Sagar Behere, and Dennis Park
United States Patent \#11157756. October 2021.

\bibitem{P7}``Actively Adapting To Driving Environments Based On Human Interactions''.
Soonho Kong, Jonathan DeCastro, Nikos Arechiga, and Frank Permenter
United States Patent \#11072342. July 2021.

\bibitem{P8} ``Systems And Methods For Improving Situational Awareness Of A User''.
Jonathan DeCastro, Frank Permenter, Soonho Kong, and Nikos Arechiga
United States Patent \#10621858. April 2020.

\end{thebibliography}


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \mysection{Honors \amper Awards}
% \textbf{Kwanjeong Scholarship} \hfill \interval{Aug 2010}{May 2015}\\
% Kwanjeong Education Foundation
% \vspace{0.3em}

% \textbf{National Graduate Science \amper Technology Scholarship} \hfill \interval{Sep 2008}{Aug 2009}\\
% Korea Student Aid Foundation(KOSAF)
% \vspace{0.3em}

% \textbf{Brain Korea 21 Global Internship (MSR \amper MSRA)} \hfill \interval{Aug 2008}{Nov 2008}\\
% Korea Research Foundation \hfill \interval{Aug 2007}{Feb 2008}\\
% \vspace{-0.6em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{Professional Activities}
Program Committee Member:\\
 ADHS 2021,
 HSCC 2021,
 MEMOCODE 2021,
 MT-CPS 2021,
 HSCC 2020,
 MEMOCODE 2020,
 DARS 2019,
 HSCC 2019,
 MEMOCODE 2019,
 NSV 2019,
 DARS 2018,
 WSC 2018
\\\\
External Reviewer:\\
IEEE-IV 2021, IEEE-IV 2020, POPL 2020, ATVA 2015, ASE 2014, FoSSaCS 2013, POPL 2013, APLAS 2012, SAS 2012,
GPCE 2010, SPLASH 2010, CAV 2010, VMCAI 2010, SAS 2009, DEFECTS 2009, APLAS 2007

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \mysection{References}
% \hspace{-0.25cm}
% \begin{tabular}{ll}
% \begin{minipage}[t]{0.47\textwidth}
% \textbf{Edmund M. Clarke}\\
% Professor\\
% Computer Science Department\\
% Carnegie Mellon University\\
% Email: {\small \url{emc@cs.cmu.edu}}\\
% \end{minipage}
% &
% \begin{minipage}[t]{0.47\textwidth}
% \textbf{Leonardo de Moura}\\
% Principal Researcher\\
% Research in Software Engineering Group\\
% Microsoft Research\\
% Email: {\small \url{leonardo@microsoft.com}}\\
% \end{minipage}
% \\
% \begin{minipage}[t]{0.47\textwidth}
% \textbf{Kwangkeun Yi}\\
% Professor\\
% School of Computer Science\\
% Seoul National University\\
% Email: {\small \url{kwang@ropas.snu.ac.kr}}\\
% \end{minipage}
% &
% \begin{minipage}[t]{0.47\textwidth}
% \textbf{Jeremy Avigad}\\
% Professor\\
% Department of Philosophy and the Department of Mathematical Sciences\\
% Carnegie Mellon University\\
% Email: {\small \url{avigad@cmu.edu}}\\
% \end{minipage}
% \end{tabular}
% \hrulefill

\vfill
\begin{center}
{\footnotesize
  Last updated: \today \\
  \url{https://soonhokong.github.io/cv.pdf}
}
\end{center}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
